Apache Storm

### 2017-12-01 paper.tex
Added Topology info

\subsubsection{Topology}
\paragraph{Topology} is a directed graph where the vertices represent computation and the edges represents the data flow.

>>>>

\subsubsection{Topology}
\paragraph{Topology} is a directed graph where the vertices represent computation and the edges represents the data flow. Another important thing about topologies in Storm is that they are allowed to have cycles. Figure \ref{fig:topo} shows a basic Storm Topology, which consists of Spouts and Bolts. Spouts are the Sources of tuples in a Topology whereas Bolts are the units which process these generated tuples. The user first submits the topology to the Apache Storm Nimbus, which consults with each of the available Supervisors in the worker nodes and assigns each of them with tasks related to the topology.

\begin{figure}
  \begin{center}
    \includegraphics[width=.7\textwidth]{topo.png}
    \caption{Generic Storm Topology}
    \label{fig:topo}
   \end{center}
\end{figure}

\paragraph{Spout} is the entry point for any data in the Storm Topology. As shown in the figure \ref{fig:topo} spouts take data from external source and emits them into the topology as tuples. The input source could be a Heterogenous data source.

\paragraph{Bolt} are the processing entities of a Topology. It receives raw tuples emitted by spouts or processed tuples sent by another bolt and sends it down the pipe after it has completed its processing.
